The evolution of gene expression in the term placenta of viviparous mammals

### 2016-12-01 presentation/placenta_viviparous_presentation.Rnw
fix axis italics after coord flip

\begin{frame}{Transcriptome Mapping Statistics: Unmapped}
\begin{figure}
<<transcriptome.mapping.figure.unmapped,fig.width=8,fig.height=8,echo=FALSE>>=
star.logs.unmapped <- 
    star.logs[grepl("%",field) & 
                  grepl("unmapped",field) & 
                      !grepl("too many mismatches",field),]
star.logs.unmapped <- 
    star.logs.unmapped[,field:=capfirst(gsub("\\% of reads unmapped: ","",field))]
print(ggplot(star.logs.unmapped,
             aes(x=capfirst(species),y=as.numeric(gsub("%","",value))))
      + geom_boxplot()
      + facet_grid(field~.)
      + ylab("Percent of Reads")
      + xlab("Species")
      + theme_bw()
      + coord_flip()
      + theme(legend.position="top",
              axis.text.x = element_text(face="italic"))
      )
@ 
\end{figure}
\end{frame}

>>>>

\begin{frame}{Transcriptome Mapping Statistics: Unmapped}
\begin{figure}
<<transcriptome.mapping.figure.unmapped,fig.width=8,fig.height=8,echo=FALSE>>=
star.logs.unmapped <- 
    star.logs[grepl("%",field) & 
                  grepl("unmapped",field) & 
                      !grepl("too many mismatches",field),]
star.logs.unmapped <- 
    star.logs.unmapped[,field:=capfirst(gsub("\\% of reads unmapped: ","",field))]
print(ggplot(star.logs.unmapped,
             aes(x=capfirst(species),y=as.numeric(gsub("%","",value))))
      + geom_boxplot()
      + facet_grid(field~.)
      + ylab("Percent of Reads")
      + xlab("Species")
      + theme_bw()
      + coord_flip()
      + theme(legend.position="top",
              axis.text.y = element_text(face="italic"))
      )
@ 
\end{figure}
\end{frame}
